The Next Generation of Canadian Salmon

### 2024-04-19 output/paper.qmd
add modelsummaries

To create the linear model we made use of the `rstanarm` [@citerstanarm] package.

@@

@@

```{r}
# TODO modelsummary
```

@@

```{r}
# TODO modelsummary
```

# Results

>>>>

To create the linear model we made use of the `rstanarm` [@citerstanarm] package, and to summarize the results we made use of the `modelsummary` [@citemodelsummary] package.

@@

# Load in models
yearly_change_model <-
  readRDS(file = "models/yearly_change_model.rds")

catch_population_model <-
  readRDS(file = "models/catch_population_model.rds")

@@

@tbl-catchmodel shows a model summary for this model, this will be discussed further in the [results](#results) section.

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: tbl-catchmodel
#| tbl-cap: "Predicting the Salmon Population given commercial fishing catch estimates"

modelsummary(
  list(
    "Salmon Population" = catch_population_model
  ),
  statistic = "mad"
  )

@@

@tbl-yearlymodel shows a model summary for this model, this will be discussed in the [results](#results) section.

```{r}
#| message: false
#| warning: false
#| echo: false
#| label: tbl-yearlymodel
#| tbl-cap: "Predicting the Salmon Population in 4 years time given a year's spawn statistics"

modelsummary(
  list(
    "Salmon Population" = yearly_change_model
  ),
  statistic = "mad"
  )

# Results {#results}
